Assignment 4

### 2015-03-09 rmtw/a4/latex8.tex
sfa

\Section{Methodology}
This section will describe which statistical tests were used, and why. The level of significance used for all tests is 5\%.

\SubSection{Tests Used for H\textsubscript{eff} and H\textsubscript{rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The KS and SW tests both reported p-values < 0.05 and thus the null hypotheses of the data being normally distributed was rejected. See Table 1 for the results of the KS and SW tests.

\begin{table}
	\centering
	\begin{tabular}[ht]{| l | l | l |}
	\hline
	Test & Sample & p-value  \\
	\hline
	KS & UC & =< 2.2e-16 \\
	\hline
	SW & UC & 0.000969 \\
	\hline
	KS & CL & =< 2.2e-16 \\
	\hline
	SW & CL & 0.309 \\	
	\hline
	\end{tabular}
	\caption{Results of normality tests}
\end{table}

@@

\begin{figure}[Ht!]
\centering
\includegraphics[width=90mm]{uc_qq.png}
\caption{Use Case Q-Q plot}
\end{figure}

\begin{figure}[Ht!]
\centering
\includegraphics[width=90mm]{cl_qq.png}
\caption{Checklist Q-Q plot}
\end{figure}

>>>>

\Section{Methodology}
This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05.

\SubSection{Tests Used for H\textsubscript{eff} and H\textsubscript{rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The data used for the tests was the number faults found by each participant. The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{eff} and H\textsubscript{rate}. The KS and SW tests both reported p-values < 0.05. See Table 1 for the p-values of the KS and SW tests. The critical value analysis for the KS and SW showed similar results and thus the null hypotheses of the data being normally distributed was rejected. See Table 2 for more information about the critical value results of the KS and SW tests.

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l |}
	\hline
	Test & Sample & p-value  \\
	\hline
	KS & UC & \textless 2.2e-16 \\
	\hline
	SW & UC & 0.000969 \\
	\hline
	KS & CL & \textless 2.2e-16 \\
	\hline
	SW & CL & 0.309 \\	
	\hline
	\end{tabular}
	\caption{KS \& SW tests - p-value}
\end{table}

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l |}
	\hline
	Test & Sample & Critical Value & D (result)  \\
	\hline
	KS & UC & 0.270 & 0.9388 \\
	\hline
	SW & UC & 0.964 &  0.8412 \\
	\hline
	KS & CL & 0.270 & 0.9388 \\
	\hline
	SW & CL & 0.964 & 0.9553 \\	
	\hline
	\end{tabular}
	\caption{KS \& SW tests - Critical Value}
\end{table}

@@

\begin{figure}[Ht]
\centering
\includegraphics[width=90mm]{uc_qq.png}
\caption{Use Case Q-Q plot}
\end{figure}

\begin{figure}[Ht]
\centering
\includegraphics[width=90mm]{cl_qq.png}
\caption{Checklist Q-Q plot}
\end{figure}
